### 2019-02-07 thesis/2_chapters/chap1.tex
Update thesis Feb 7

\noindent Nanosatellite is a small artificial satellite with a wet mass(the total mass of the hardware plus fuel and oxidizer) between 1 – 10 kg. Nanosatellites are cheap but capable of performing commercial missions and has led researchers and scientists to explore the new way to use the Nanosatellites in LEO\cite{network}. Their designs are only comprised of low-cost components. Due to their cost-effective, fast development cycle and size convenience, Nanosatellites are becoming popular in educational and scientific development. Nanosatellites can be quickly built in a small university project. \\

@@

Another way of attitude determination approach is using star trackers. Star Tracker is an optical-electronics subsystem comprises of a CCD or CMOS Image sensor attached to an optical lens and a computing system, usually a microprocessor integrated into an ASIC board. The image sensor will firstly take an image of multiple star clusters at a specific fixed orientation. After that, the image is processed through the computing system to extract a particular feature of the model depending on a predefined algorithm. Then, the specific feature is compared with a prebuilt pattern or feature database stored in the memory. The output of the algorithm is often a star ID, which has a specific attitude, this attitude is again used to determine the attitude(orientation) of the spacecraft. \\

@@

% Section 1.3
\section{Major contributions}
The following are the significant contributions of this research project.
\begin{itemize}
	\item Investigates and Analyses the star tracking algorithms on the advantages and weaknesses of traditional methods.
	\item Reviews and examines in details the proposed algorithm by precedent research.
	\item Implements the proposed method in term of hardware and software co-processing approach on an embedded system for star tracker.
\end{itemize}

% Section 1.4
\section{Organization of the thesis}
The rest of the thesis is organized as followed:
\begin{itemize}
	\item Chapter 2: Introduces the basis of star tracking operation, reviews some of the state of the art star tracking algorithms and the chosen algorithm to be implemented by the software-hardware co-processing approach.
	\item Chapter 3: Introduces and analyzes a proposed algorithm to be implemented on the hardware.
	\item Chapter 4: Discusses the result of the implementation regarding runtime performance and hardware resources.
\end{itemize}

>>>>

\noindent Nanosatellite is a small artificial satellite with a wet mass(the total mass of the hardware plus fuel and oxidizer) between 1 - 10 kg. Nanosatellites are cheap but capable of performing commercial missions and has led researchers and scientists to explore the new way to use the Nanosatellites in LEO\cite{network}. Their designs are only comprised of low-cost components. Due to their cost-effective, fast development cycle and size convenience, Nanosatellites are becoming popular in educational and scientific development. Nanosatellites can be quickly built in a small university project. \\

@@

Another way of attitude determination approach is using star trackers\cite{edseee.38797119950101}. Star Tracker is an optical-electronics subsystem comprises of a CCD or CMOS Image sensor attached to an optical lens and a computing system, usually a microprocessor integrated into an ASIC board. The image sensor will firstly take an image of multiple star clusters at a specific fixed orientation. After that, the image is processed through the computing system to extract a particular feature of the model depending on a predefined algorithm. Then, the specific feature is compared with a prebuilt pattern or feature database stored in the memory. The output of the algorithm is often a star ID, which has a specific attitude, this attitude is again used to determine the attitude(orientation) of the spacecraft. \\

@@

% Section 1.3
\section{Major contributions}
The major contributions of this research project are summarized as follows:
\begin{itemize}
	\item First, we review three classic star tracking algorithms which are applying in commercial star trackers. Analyzing and comparing their strengths and weaknesses. We then discuss the novel star tracking algorithm presented in ``An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance'' by M.D. Pham, K.S. Low and S.H. Chen\cite{edselc.2-52.0-8487677997120120101,edseee.655799920130101}, introduce the steps of the algorithm and explain why the algorithm is suitable for applying in nano-satellites compared to the three classic star tracking algorithms and chosen to be implemented by the hardware-software co-processing approach.
	\item Based on the algorithm analysis, we partition the algorithm into submodules and propose which part should be implemented on the software part or the hardware part. Our main contribute includes (a) an optimized star tracking algorithm for hardware-software co-processing approach, (b) a star tracking embedded system for nano-satellites. 
\end{itemize}

% Section 1.4
\section{Organization of the thesis}
The rest of the thesis is organized as followed:
\begin{itemize}
	\item Chapter 2: Introduces the basis of star tracking operation, reviews some of the state of the art star tracking algorithms and the chosen algorithm to be implemented by the software-hardware co-processing approach.
	\item Chapter 3: Introduces and analyzes a proposed algorithm to be implemented on the hardware.
	\item Chapter 4: Discusses the result of the implementation regarding runtime performance and hardware resources.
	\item Chapter 5: Summarizes the work and proposes future research topics.
\end{itemize}

### 2019-02-07 thesis/2_chapters/chap2.tex
Update thesis Feb 7

The star tracking algorithm operates mainly in 2 different modes: the Lost in Space (LIS) and Tracking modes:
\begin{itemize}
	\item LIS mode: the initial attitude is unknown, the star tracker must determine it which is the most critical part of the star tracking operation. LIS mode is operated at the time when the power system is switched on or reset after an attitude determination attempt from tracking mode failed\cite{edselc.2-52.0-8487677997120120101}.
	\item Tracking mode: after the initial attitude is recognized. The star tracker is switched to the Tracking mode. With the initial is acknowledged, the computing can easily predict and track the attitude based on the previous information.
\end{itemize}

@@

The first step is to acquire the image which is accomplished by the image sensor. The image acquired has to be processed for estimating the coordinates of the stars in the image plane. This is completed by applying the centroiding process on the image. The input of this step is a star image with multiple star clusters. The output is the coordinate of every star presenting. Due to distributed energy surface, a star projection is spread over a 3x3 to 11x11 square area\cite{ntu.54658220060101}, the star projection is a group of connected pixels. Therefore, the best way to identify the star clusters is to apply the ‘connected component’ algorithm.

@@

% Table 2.1
\noindent Table~\ref{tab:starList} .\\

@@

\noindent A star pattern is spread over an area so we can calculate its centroid by applying the weighted pixel intensity technique. Assume that (i, j) is the horizontal and vertical centroid coordinate of a star, $I_{ij}$ is each pixel intensity of the star pattern, i and j are the horizontal and vertical coordinates of each pixel of the star pattern.

@@

% Equation 2.1
\noindent Equation~\ref{eq:2_1}

@@

% Equation 2.2
\noindent The star triplet will form 2 angular distances $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_2}
\begin{equation}
	\begin{aligned}
		\theta_1 = \cos(V_A, V_B) \\
		\theta_2 = \cos(V_A, V_C) \\
		\theta = \cos(V_{AB}, V_{AC})
	\end{aligned}
	\label{eq:2_2}
\end{equation}

@@

\noindent The star triplet will form 2 angular distance $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_3}
\begin{equation}
	f = \{\theta, \theta_1, \theta_2\}
	\label{eq:2_3}
\end{equation}

% Table 2.2
\noindent Table~\ref{tab:Liebe_SPD}.

\begin{ntutab}{|c|c|c|}{Liebe_SPD}{An example of Liebe star pattern database}
	\hline
	$\theta_1$ & $\theta_2$ & $\theta$ \\
	\hline
	54 & 80 & 32 \\
	54 & 80 & 33 \\
	54 & 81 & 32 \\
	54 & 81 & 33 \\
	54 & 82 & 32 \\
	54 & 82 & 33 \\
	55 & 80 & 32 \\
	55 & 80 & 33 \\
	55 & 81 & 32 \\
	55 & 81 & 33 \\
	55 & 82 & 32 \\
	55 & 82 & 33 \\
	56 & 80 & 32 \\
	56 & 80 & 33 \\
	56 & 81 & 32 \\
	56 & 81 & 33 \\
	56 & 82 & 32 \\
	56 & 82 & 33 \\
	\hline
\end{ntutab}

@@

\noindent The weakness of this algorithm is the weak robustness due to the limitation of star utilization. It only employs the three nearest stars to the centre and discards other stars which will then lead to a mismatch if the 2 predefined nearest neighboring stars does not appear in the star image. Besides, if the reference star appears in the final entry of the Star Pattern Database.

@@

% Table 2.3
\noindent Table~\ref{tab:Pyramid_pattern}.

@@

\noindent One of the advantages of the pyramid algorithm is that it employs 4 stars to build the feature vector compared to only 3 stars of the Liebe algorithm. Compared to Liebe’s, this method is more robust since it makes the star recognition process more accurate as six features are utilized for identification purpose compared to only three features used by the Liebe algorithm\cite{HETE}. \\

@@

\noindent The chosen star tracking algorithm is from the paper “An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance” by M.D. Pham, K.S. Low and S.H. Chen\cite{edselc.2-52.0-8487677997120120101,edseee.655799920130101}. The algorithm introduces a novel star pattern identification using an optimized database and proposes a search tree data structure for quick and advanced parallel search. \\

\noindent Due to the advance of the previous research have been proven, this star tracking algorithm will be chosen to be implemented on the hardware. \\

@@

\noindent To search and match the star pattern vector with the database, a special database structure is pre-built. The tree structure is built with multiple levels, the first level is N-Number of stars in the FOV, next layers will be the distances from the reference stars to all of its neighbors which are sorted ascendingly from nearest neighboring star to the farthest. \\

>>>>

The star tracking algorithm operates mainly in 2 different modes: the Lost in Space (LIS) and Tracking modes:
\begin{itemize}
	\item LIS mode: the initial attitude is unknown, the star tracker must determine it which is the most critical part of the star tracking operation. LIS mode is operated at the time when the power system is switched on or reset after an attitude determination attempt if tracking mode failed\cite{edselc.2-52.0-8487677997120120101}.
	\item Tracking mode: after the initial attitude is recognized. The star tracker is switched to the Tracking mode. With the initial is acknowledged, the computing can easily predict and track the attitude based on the previous information.
\end{itemize}

@@

The first step is to acquire the image which is accomplished by the image sensor. The image acquired has to be processed for estimating the coordinates of the stars in the image plane as shown in Figure~\ref{fig:2_2}. This is completed by applying the centroiding process on the image. The input of this step is a star image with multiple star clusters. The output is the coordinate of every star presenting. Due to distributed energy surface, a star projection is spread over a 3x3 to 11x11 square area\cite{ntu.54658220060101}, and the star projection is a group of connected pixels. Therefore, the best way to identify the star clusters is to apply the connected component algorithm.

@@

% Table 2.1
\noindent Table~\ref{tab:starList} shows how star centroids in an image, as in Figure~\ref{fig:2_4} are stored under a list of Cartesian coordinates. Besides, star trackers may use other coordinate systems like the Polar coordinate system, Cylindrical or Spherical coordinate systems.\\

@@

% Equation 2.1
\noindent A star pattern is spread over an area so we can calculate its centroid by applying the weighted pixel intensity technique. Equation~\ref{eq:2_1} shows how to calculate a star centroid in Cartesian coordinate. Assume that (x, y) is the horizontal and vertical centroid coordinate of a star cluster, $I_{ij}$ is each pixel intensity of the star pattern, i and j are the horizontal and vertical coordinates of each pixel within this star cluster.

@@

@@

% Equation 2.2
\noindent The star triplet will form 2 angular distances $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_2}. $V_A, V_B, V_C$ are the Euclidean vectors connecting each star in the star triplet with the star tracker(or the spacecraft), $V_{AB}$ is the Euclidean vector connecting star A and star B. Therefore, we have the Euclidean vector connecting star A and star C denoted by $V_{AC}$.
\begin{equation}
	\begin{aligned}
		\theta_1 = \cos(V_A, V_B) \\
		\theta_2 = \cos(V_A, V_C) \\
		\theta = \cos(V_{AB}, V_{AC})
	\end{aligned}
	\label{eq:2_2}
\end{equation}

@@

\begin{equation}
	f = \{\theta_1, \theta_2, \theta\}
	\label{eq:2_3}
\end{equation}

% Table 2.2
\noindent Table~\ref{tab:Liebe_SPD} shows an example of Liebe star pattern database. Each feature vector $f = \{\theta_1, \theta_2, \theta\}$ would return a corresponding star ID which identify the identification of the reference star. Thus, The table is sorted for quick searching purpose. \\

\begin{ntutab}{|c|c|c|c|}{Liebe_SPD}{An example of Liebe star pattern database}
	\hline
	$\theta_1$ & $\theta_2$ & $\theta$ & Star ID \\
	\hline
	54 & 80 & 32 & 55 \\
	54 & 80 & 33 & 631 \\
	54 & 81 & 32 & 114 \\
	54 & 81 & 33 & 1297 \\
	54 & 82 & 32 & 611 \\
	54 & 82 & 33 & 168 \\
	55 & 80 & 32 & 284 \\
	55 & 80 & 33 & 811 \\
	55 & 81 & 32 & 1289 \\
	55 & 81 & 33 & 6 \\
	55 & 82 & 32 & 602 \\
	55 & 82 & 33 & 1165 \\
	56 & 80 & 32 & 222 \\
	56 & 80 & 33 & 327 \\
	56 & 81 & 32 & 470 \\
	56 & 81 & 33 & 104 \\
	56 & 82 & 32 & 1058 \\
	56 & 82 & 33 & 1222 \\
	\hline
\end{ntutab}

@@

\noindent The weakness of this algorithm is the weak robustness due to the limitation of star utilization. It only employs the three nearest stars to the centre and discards other stars which will then lead to a mismatch if the two predefined nearest neighboring stars do not appear in the star image. Besides, if the reference star appears in the final entry of the Star Pattern Database, the searching algorithm would fall into the worst case.

@@

@@

\noindent One of the advantages of the pyramid algorithm is that it employs 4 stars to build the feature vector compared to only 3 stars of the Liebe algorithm. Compared to Liebe’s, this method is more robust since it makes the star recognition process more accurate as six features (as denoted in Equation~\ref{eq:2_4}) are utilized for identification purpose compared to only three features used by the Liebe algorithm\cite{HETE}. The Table~\ref{tab:Pyramid_pattern} describes how the star patterns $p_1, p_2, p_3, p_4, p_5, p_6$ are defined by angular distances between Star 1 and Star 2. \\

@@

\noindent The chosen star tracking algorithm is from the paper ``An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance'' by M.D. Pham, K.S. Low and S.H. Chen\cite{edselc.2-52.0-8487677997120120101,edseee.655799920130101}. The algorithm introduces a novel star pattern identification using an optimized database and proposes a search tree data structure for quick and advanced parallel search. \\

@@

\noindent To search and match the star pattern vector with the database, a special the tree structured database is pre-built. Figure~\ref{fig:2_9} shows an example of this tree structured database. The tree is built with multiple levels, the first level is N-Number of stars in the FOV, next layers will be the distances from the reference stars to all of its neighbors which are sorted ascendingly from nearest neighboring star to the farthest. \\

### 2019-02-07 thesis/2_chapters/chap3.tex
Update thesis Feb 7

\noindent \textbf{LUTs}: FPGAs were first designed to imitate Gate Arrays – integrated circuits with a sea of gates that were connected by added metal layers (wire routing) to define the functionality of the device. However, instead of implementing the logic using transistor gates, the logic was in many cases implemented by memory fashioned as look up tables. \\

@@

\noindent \textbf{Routing}: The routing in an FPGA is hierarchical. At the lowest level, we have a routing switch that is controlled by a bit of SRAM, or a FLASH bit, or a fuse. There are many routing switches in the local routing to connect various logic elements or blocks. The FPGA is made of a sea of these logic blocks. Groups of the blocks are connected by long lines or very long lines. Common signals like clocks are routed on special routing networks called global networks. \\

@@

\noindent \textbf{FPGA design flow}: The design begins with design entry, continues with simulation to verify the logic is implemented as expected, and then the tool will perform synthesis (also called mapping) to map the logic to the device architecture. Next the tool will create the interconnection between cells by placing and routing (or fitting) the design. Another simulation after the fitting is done is a good practice. If this looks good, the next step to use the tool to create a programming file, which is then downloaded into the FPGA device for testing\cite{Coursera}. \\

@@

\ntuepsfig[width=\textwidth]{3_spartan}{Xilinx Spartan-3AN Family Architecture\cite{spartan}}

@@

\pagebreak 
\subsection{System-on-a-chip}

@@

\noindent Traditional SoC board is a fixed Application Specific Integrated Circuit (ASIC) which is prebuilt for only one particular function or task. The processing time of ASIC board is fast and highly efficient due to the unique hardware prebuilt for this task. In the trade-off, the development time of an ASIC board takes much longer due to multiple stages of hardware synthesis, testing and verification and the cost of development is enormous. ASIC board is only suitable for mass-production strategy with over 1 million products per development cycle. \\

@@

\noindent Another approach is using an embedded processor for the implementation. All stages of the development are equivalent to a software development process. This approach brings some advantages like low-cost development, flexibility, easy to fix and testing, short-time-development, and short-time-to-market. On the downside, the approach of using multipurpose processors causes high power consumption, low efficiency in the product operation. \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 3.2
\section{Partition and Profiling}

@@

Partitioning is the first stage of PSoC development. The algorithm or the program will be partitioned into suitable-size submodules. These submodules are later decided to be implemented on which side of the PSoC: Programmable Logics or Processing System. How the program is partitioned, decided by the designer. \\

@@

Profiling is a practical analysis that measures and analyze the space and time complexity of an algorithm or a submodule of an algorithm. By examine the profiling result, we can specify the most critical time-consuming part or module of the system. Then based on the profiling and asymptotic analysis stated above, we can decide correctly which parts or submodules can be implemented in hardware instead of software. \\

@@

% Table 3.1
\noindent Table~\ref{tab:profiling}.

\begin{ntutab}{|c|c|}{profiling}{Module Profiling Result}
	\hline
	\textbf{Modules} & \textbf{Runtime(nanoseconds)} \\
	\hline
	Centroiding & 17688 \\
	\hline
	Choose Reference Star & 54 \\
	\hline
	Find the star pattern & 30 \\
	\hline
	Pattern matching (with tree database) & 20 \\
	\hline
\end{ntutab}

@@

In the first stage, the sky is captured by a Charge-coupled device(CCD) through lens then discretized into digital star images. In which, each pixel is an 8-bit integer value which represents the intensity or brightness of a pixel(0 represents darkest pixel and 255 represents the brightest pixel). The star image is usually contaminated with noise as a result of dark current noise and non-star stellar object. Dark current noise arises from thermal energy within the silicon lattice. It can be represented as a background image generated by a certain period of exposure with the shutter closed\cite{MDP}. To eliminate the noise and separate star clusters from the background, we apply thresholding technique. The threshold level can be chosen by averaging all pixel intensities. The pixel which has a higher value than threshold level belongs to a star cluster while the pixel which has a lower value than the threshold belongs to the background. Figure~\ref{fig:3_10} shows how to separate star clusters from the background, the threshold, in this case, is 70.

@@

The one-pass scan algorithm is a connected component labeling approach which performs a scanning throughout the star image. A pixel in a star cluster will be put into an equivalent independent subset if two subsets having pixels connected to each other will be merged into one big set by the applying the following rules. \\

\noindent We maintain a disjoint set data structure when scanning performed if a pixel P is non-background, we consider its left and above pixels as in Figure~\ref{fig:3_11}. There are 3 cases:

@@

\noindent In figure~\ref{fig:3_17}, the pixel coordinates(i,j) in 2D images would be represented by the stream order(k). The reason we need to have a converting framework is that we need to look up the above and left pixels of a considering pixel in the one-pass scan algorithm. \\

@@

\noindent The converting equations:
	$$k = i*ImgHeight + j$$
	$$i = k / ImgHeight$$
	$$j = k mod ImgHeight$$

>>>>

\noindent \textbf{LUTs}: FPGAs were first designed to imitate Gate Arrays – integrated circuits with a sea of gates that were connected by added metal layers (wire routing) to define the functionality of the device. However, instead of implementing the logic using transistor gates, the logic was in many cases implemented by memory fashioned as look up tables. Figure~\ref{fig:3_LUT} shows an example of a Look up table implementing a 4-input logic function $F = (A \wedge B) \vee (C \wedge \bar{D})$. Instead of connecting the logic gates, the Lookup table memorizes the output result corresponding to the input combinations. \\

@@

\noindent \textbf{Routing}: The routing in an FPGA is hierarchical. At the lowest level, we have a routing switch that is controlled by a bit of SRAM, or a FLASH bit, or a fuse. There are many routing switches in the local routing to connect various logic elements or blocks. The FPGA is made of a sea of these logic blocks. Groups of the blocks are connected by long lines or very long lines. Common signals like clocks are routed on special routing networks called global networks. The FPGA routing architecture is demonstrated in Figure~\ref{fig:3_Routing}\\

@@

\noindent \textbf{FPGA design flow}: The design begins with design entry, continues with simulation to verify the logic is implemented as expected, and then the tool will perform synthesis (also called mapping) to map the logic to the device architecture. Next the tool will create the interconnection between cells by placing and routing (or fitting) the design. Another simulation after the fitting is done is a good practice. If this looks good, the next step to use the tool to create a programming file, which is then downloaded into the FPGA device for testing\cite{Coursera}. The FPGA design flow is presented in Figure~\ref{fig:3_DesignFlow} \\

@@

\ntuepsfig[width=4in]{3_spartan}{Xilinx Spartan-3AN Family Architecture\cite{spartan}}

@@

% \pagebreak 
\subsection{System-on-a-chip}

@@

\noindent Traditional SoC board is a fixed Application Specific Integrated Circuit (ASIC) (Figure~\ref{fig:3_1}) which is prebuilt for only one particular function or task. The processing time of ASIC board is fast and highly efficient due to the unique hardware prebuilt for this task. In the trade-off, the development time of an ASIC board takes much longer due to multiple stages of hardware synthesis, testing and verification and the cost of development is enormous. ASIC board is only suitable for mass-production strategy with over 1 million products per development cycle. \\

@@

\noindent Another approach is using an embedded processor(Figure~\ref{fig:3_2}) for the implementation. All stages of the development are equivalent to a software development process. This approach brings some advantages like low-cost development, flexibility, easy to fix and testing, short-time-development, and short-time-to-market. On the downside, the approach of using multipurpose processors causes high power consumption, low efficiency in the product operation. \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 3.2
\section{Partition and Profiling}

@@

Partitioning is the first stage of PSoC development. The algorithm or the program will be partitioned into suitable-size submodules. These submodules are later decided to be implemented on which side of the PSoC: Programmable Logics or Processing System as illustrated in Figure~\ref{fig:3_5}. How the program is partitioned, decided by the designer. \\

@@

Profiling is a practical analysis that measures and analyze the space and time complexity of an algorithm or a submodule of an algorithm. By examine the profiling result, we can specify the most critical time-consuming part or module of the system. Then based on the profiling and asymptotic analysis stated above, we can decide correctly which parts or submodules can be implemented in hardware instead of software. The profiling steps \\

@@

% Table 3.1
% \noindent Table~\ref{tab:profiling}.

% \begin{ntutab}{|c|c|}{profiling}{Module Profiling Result}
% 	\hline
% 	\textbf{Modules} & \textbf{Runtime(nanoseconds)} \\
% 	\hline
% 	Centroiding & 17688 \\
% 	\hline
% 	Choose Reference Star & 54 \\
% 	\hline
% 	Find the star pattern & 30 \\
% 	\hline
% 	Pattern matching (with tree database) & 20 \\
% 	\hline
% \end{ntutab}

@@

In the first stage, the sky is captured by a Charge-coupled device(CCD) through lens then discretized into digital star images. In which, each pixel is an 8-bit integer value which represents the intensity or brightness of a pixel(0 represents darkest pixel and 255 represents the brightest pixel). The star image is usually contaminated with noise as a result of dark current noise and non-star stellar object. Dark current noise arises from thermal energy within the silicon lattice. It can be represented as a background image generated by a certain period of exposure with the shutter closed\cite{MDP}. To eliminate the noise and separate star clusters from the background, we apply thresholding technique. The threshold level can be chosen by averaging all pixel intensities. The pixel which has a higher value than threshold level belongs to a star cluster while the pixel which has a lower value than the threshold belongs to the background. Figure~\ref{fig:3_10} shows how to separate star clusters from the background. \\

\noindent Most of the star images are affected by noise. Sometimes, the star tracker misleads the noise as a star which often leads to a mismatch. Therefore, the threshold should be carefully chosen. If we set the threshold too low, it would lead to mismatches. Otherwise, if we set the threshold too high, some stars would be missing from the image. Between 0-255, we choose the threshold value 70 which mostly produce high matching accuracy.

@@

The one-pass scan algorithm is a connected component labeling approach which performs a scanning throughout the star image. Each star cluster is equivalent to each disjoint set. While scanning the picture, we try to identify which star pixel is corresponding to which disjoint set by applying the following rules. \\

\noindent If the pixel value is higher than the defined threshold which distinguish between the star pixel and the background of the image, we consider its left and above pixels as in Figure~\ref{fig:3_11}. There are 3 cases:

@@

\noindent In figure~\ref{fig:3_17}, the pixel coordinates(i,j) in 2D images would be represented by the stream order(k). The reason we need to have a converting framework is that we need to look up the above and left pixels of the pixel in the one-pass scan algorithm. \\

@@

\noindent The converting equations:
	$$k = i*ImgHeight + j$$
	$$i = k / ImgHeight$$
	$$j = k\ mod\ ImgHeight$$
